IMPC Mouse data - Variance in sex differences

### 2019-11-21 scripts/2019_Nov1-FiguresRearranged_IMPC_variance_and_sex_difference.Rmd
Clean up: looping across traits

Loop running meta-analysis on all traits
The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance. Those traits will be removed in later steps, outlined below.

@@

#Create dataframe to store results

results_alltraits_grouping <- 
    tibble(id = 1:n, lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, 
           lnCVR_se=0, lnVR=0, lnVR_lower=0, lnVR_upper=0, 
           lnVR_se=0, lnRR=0, lnRR_lower=0, lnRR_upper=0, lnRR_se=0, sampleSize=0, trait=0)

for (t in 1:n) {
  tryCatch(
    {

      data_par_age <- data_subset_parameterid_individual_by_age(data, t, age_min = 0, age_center = 100)
      population_stats <- calculate_population_stats(data_par_age)

@@

      results_alltraits_grouping[t, 2] <- cvr$b
      results_alltraits_grouping[t, 3] <- cvr$ci.lb
      results_alltraits_grouping[t, 4] <- cvr$ci.ub
      results_alltraits_grouping[t, 5] <- cvr$se

      cvr

      # lnVR, comparison of standard deviations

      cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR,
                            random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
                            control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
                                           maxit = 1000), 
                            verbose = F, data = results)

      results_alltraits_grouping[t, 6] <- cv$b
      results_alltraits_grouping[t, 7] <- cv$ci.lb
      results_alltraits_grouping[t, 8] <- cv$ci.ub
      results_alltraits_grouping[t, 9] <- cv$se

      # for means, lnRR

      means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, 
                               random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
                               control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
                                              maxit = 1000), 
                               data = results)
      results_alltraits_grouping[t, 10] <- means$b
      results_alltraits_grouping[t, 11] <- means$ci.lb
      results_alltraits_grouping[t, 12] <- means$ci.ub
      results_alltraits_grouping[t, 13] <- means$se

      results_alltraits_grouping[t, 14] <- means$k
      results_alltraits_grouping[t, 15] <- unique(results$trait)
    },
    error = function(e) {
      cat("ERROR :", conditionMessage(e), "\n")
    }
  )
}

# Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance. We'll export and use this in the Shiny App. **Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**

@@

# trait_meta_results <- write.csv(results_alltraits_grouping, file = "export/trait_meta_results.csv")
```

>>>>

Loop running meta-analysis on all traits

* The loop combines the functions mentioned above and fills the data matrix with results from our meta analysis. 
* Error messages indicate traits that either did not reach convergence, or that did not return meaningful results in the meta-analysis, due to absence of variance. Those traits will be removed in later steps, outlined below.

@@

# Create dataframe to store results
results_alltraits_grouping <- 
    tibble(id = 1:n, lnCVR=0, lnCVR_lower=0, lnCVR_upper=0, 
           lnCVR_se=0, lnVR=0, lnVR_lower=0, lnVR_upper=0, 
           lnVR_se=0, lnRR=0, lnRR_lower=0, lnRR_upper=0, lnRR_se=0, sampleSize=0, trait=0)

for (t in 1:n) {
  tryCatch(
    {
      results <- data %>% 
        data_subset_parameterid_individual_by_age(t) %>%
        calculate_population_stats() %>%
        create_meta_analysis_effect_sizes()

@@

      # lnVR, comparison of standard deviations
      cv <- metafor::rma.mv(yi = effect_size_VR, V = sample_variance_VR,
                            random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
                            control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
                                           maxit = 1000), verbose = F, data = results)

      # for means, lnRR
      means <- metafor::rma.mv(yi = effect_size_RR, V = sample_variance_RR, 
                               random = list(~ 1 | strain_name, ~ 1 | production_center, ~ 1 | err), 
                               control = list(optimizer = "optim", optmethod = "Nelder-Mead", 
                                              maxit = 1000), verbose = F, data = results)

      f <- function(x) unlist(x[c("b", "ci.lb", "ci.ub", "se")])

      results_alltraits_grouping2[t, 2:15] <- 
        c(f(cvr), f(cv), f(means), means$k, unique(results$trait))
    },
    error = function(e) {
      cat("ERROR :", conditionMessage(e), "\n")
    }
  )
}
```

Now that we have a "results" table with each of the meta-analytic means for all effect sizes of interest, we can use this table as part of the Shiny App, which will then be able to back calculate the percentage differences between males and females for mean, variance and coefficient of variance. We'll export and use this in the Shiny App. **Note that I have not dealt with convergence issues in some of these models, and so, this will need to be done down the road**

@@

# trait_meta_results <- write.csv(results_alltraits_grouping, file = "export/trait_meta_results.csv")
